Blockchain System

### 2020-08-25 papers/execution-model/model.tex
update

\begin{document}
\maketitle

@@

\begin{equation}{}
\frac{\text{checkBan(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ checkPub(\MANAGERS, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$}\\
\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [($<$ transfer $n$ from $puk$ to $puk'$ fee $m$, generateOph($pkh$, }\\
\text{$pkh', n, m$, \TIME), \TIME $>$) :: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 3 [rejected of counter]:

@@

\begin{equation}{}
\frac{\text{$\neg$ checkBan(\MANAGERS, $pkh, m, n$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$ }\\
\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 5 [rejected of public key]:

\begin{equation}{}
\frac{\text{$\neg$ checkPub(\MANAGERS, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$ }\\
\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 6 [included]:
\begin{equation}{}
\frac{}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puk'$ fee $m$, oph, \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$ } \\
 \text{[\PENDING, $<$ transfer $n$ from  $puk$ to $puk'$ fee $m$, oph, \TIME' $>$ :: \ACCEPTED, updateSucc(\MANAGERS, } \\
\text{$puk, puk', n, m$), \CONTRACTORS, \TIME' + 1]}}} 
\end{equation}
~\\
Rule 7 [timeout]:
\begin{equation}{}
\frac{\text{\TIME' - \TIME $\ge$ 60}}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puk'$ fee $m$, oph, \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$} \\
 \hspace*{0cm} \text{[\PENDING, \ACCEPTED, updateCou(\MANAGERS, $puk$, False), \CONTRACTORS, \TIME']}}} 
\end{equation}

@@

\begin{equation}{}
\frac{\text{checkBan(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ \text{checkPrg($code, s$)}}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{ :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] $\rangle \rightarrow \langle$ [\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[(originate contract ${id}$ transferring ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), \CONTRACTORS, \TIME] $\rangle$}}} 
\end{equation}
~\\
~\\
Rule 3 [rejected of code]:

@@

\begin{equation}{}
\frac{\text{$\neg$ checkBan(\MANAGERS, $pkh, n, m$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 6 [included]:
\begin{equation}{}
\frac{}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [$<$ (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running } \\
\text{${code}$ init ${s}$), \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ]$\rangle \rightarrow \langle$[\ACCOUNTS, \OPERATIONS,($< id$, } \\
\text{generateHash($id, code, s$, \TIME'), $code >$ :: \CONTRACTS)], [\PENDING, $<$ (originate contract ${id}$ } \\
\text{transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$), \TIME' $>$ :: \ACCEPTED, updateSucc(\MANAGERS, } \\
\text{$puk, n, m$), ($<$ generateHash($id, code, s$, \TIME'), $n, code$, } \\
 \text{getStorage($code, s$) $>$) :: \CONTRACTORS), \TIME' + 1]$\rangle$}}} 
\end{equation}
~\\
Rule 7 [timeout]:
\begin{equation}{}
\frac{\text{\TIME' - \TIME $\ge$ 60}}{\parbox{4.2in}{\text{[$<$ (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$) $>$ } \\
\text{:: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$[\PENDING, \ACCEPTED, updateCou(\MANAGERS, $puk$, False), \CONTRACTORS, \TIME']}}} 
\end{equation}
~\\
~\\
B. \textbf{Transfer}
\\
~\\
Rule 1 [proposal]:

@@

\begin{equation}{}
\frac{\text{checkBan(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ checkPuh(\CONTRACTORS, $puh$)}
\\
\text{ $\wedge$ checkArg(\CONTRACTORS, $puh, s$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}\\
\text{$\rightarrow$  $\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [($<$ (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$), }\\
 \text{generateOph($pkh, puh, s, n, m$, \TIME), \TIME $>$) :: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), }\\
\text{\CONTRACTORS, \TIME] $\rangle$}}} 
\end{equation}
~\\
~\\
Rule 3 [rejected of counter]:

@@

\begin{equation}{}
\frac{\text{$\neg$ checkBan(\MANAGERS, $pkh, n, m$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$ }\\
\text{$\rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 5 [rejected of public hash]:

@@

\begin{equation}
\frac{}{
  \begin{array}{l}
\text{[$<$ transfer $n$ from $puk$ to  $puh$ fee $m$, oph, \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$ } \\
\text{[\PENDING, $<$ (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$), oph, \TIME' $>$ :: \ACCEPTED, } \\
\text{updateSucc(\MANAGERS, puk, '', $n, m$), updateConstr(\CONTRACTORS, $puh, n$,
  $s$), $\TIME' + 1$]}
  \end{array}
}\label{eq:1}
\end{equation}
~\\
Rule 8 [timeout]:
\begin{equation}{}
\frac{\text{\TIME' - \TIME $\ge$ 60}}{\parbox{4.2in}{\text{[transfer $n$ from $puk$ to  $puh$ fee $m$, \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$} \\
\text{[\PENDING, \ACCEPTED, updatecou(\MANAGERS, $puk$, False), \CONTRACTORS, \TIME']}}} 
\end{equation}

\section{Functions}
\begin{enumerate}
    \item Function \verb!checkAcc(pkh, C)! checks whether an account $pkh$ exists in \ACCOUNTS
    \item Function \verb!checkPub(K, pkh)! checks whether the public key of the public key hash $pkh$ is reveled to the blockchain.
    \item Function \verb!checkBan(K, pkh, n, m)! checks whether the balance of the account $pkh$ is greater or equal to $m$ + $n$
    \item Function \verb!checkCou(K, pkh)! checks whether the current counter of an account $phk$ is used
    \item Function \verb!updateSuc(K, pkh, pkh', n, m)! updates the balance and the counter of the account $phk$ and the balance of the account $phk'$, where
    \begin{itemize}
        \item  \verb!< puk, pkh, bal, (n, True) >!  \verb!=>! \\ \verb!< puk, pkh, bal - n - m, (n + 1, False) >!
        \item  \verb!< puk', pkh', bal', cou' >! \verb!=>! \verb!< puk', pkh', bal' + n, cou' >!
    \end{itemize}

    \item Function \verb!updateCou(K, puk, b')! updates the counter of the account $phk$, where
    \begin{itemize}
        \item  \verb!< puk, pkh, bal, (n, b) >!  \verb!=>! \verb!< puk, pkh, bal, (n, b') >!
    \end{itemize}

@@

\begin{verbatim}
let rec updateSuc K puk puk' m n =
  match K with
  | 0 -> 0
  | < puk'', bal, cou > :: K' ->
    if (puk = puk'') then < puk'', bal - (n + m), T > 
       :: updateSuc (K', puk, puk', n, m)
    else if (puk' = puk'') then < puk'', bal + n, cou > :: K'
         else  < puk'', bal, cou > 
               ::updateSuc (K', puk, puk', n, m)
\end{verbatim}

>>>>

\begin{document}
\maketitle
\pagestyle{plain}

@@

\begin{equation}{}
\frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ checkPub(\MANAGERS, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$}\\
\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [($<$ transfer $n$ from $puk$ to $puk'$ fee $m$, generateOph($pkh$, }\\
\text{$pkh', n, m$, \TIME), \TIME $>$) :: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 3 [rejected of counter]:

@@

\begin{equation}{}
\frac{\text{$\neg$ checkBal(\MANAGERS, $pkh, m, n$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$ }\\
\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 5 [rejected of public key]:

\begin{equation}{}
\frac{\text{$\neg$ checkPub(\MANAGERS, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$ }\\
\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 6 [included]:
\begin{equation}{}
\frac{}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puk'$ fee $m$, oph, \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$ } \\
 \text{[\PENDING, $<$ transfer $n$ from  $puk$ to $puk'$ fee $m$, oph, \TIME' $>$ :: \ACCEPTED, updateSucc(\MANAGERS, } \\
\text{$puk, puk', n, m$), \CONTRACTORS, \TIME' + 1]}}} 
\end{equation}
~\\
Rule 7 [timeout]:
\begin{equation}{}
\frac{\TIME' - \TIME \ge 60}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puk'$ fee $m$, oph, \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$} \\
 \hspace*{0cm} \text{[\PENDING, \ACCEPTED, updateCou(\MANAGERS, $puk$, False), \CONTRACTORS, \TIME']}}} 
\end{equation}

@@

\begin{equation}{}
\frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ \text{checkPrg($code, s$)}}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{ :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] $\rangle \rightarrow \langle$ [\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[(originate contract ${id}$ transferring ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), \CONTRACTORS, \TIME] $\rangle$}}} 
\end{equation}
~\\
~\\
Rule 3 [rejected of code]:

@@

\begin{equation}{}
\frac{\text{$\neg$ checkBal(\MANAGERS, $pkh, n, m$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 6 [included]:
\begin{equation}{}
\frac{}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [$<$ (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running } \\
\text{${code}$ init ${s}$), \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ]$\rangle \rightarrow \langle$[\ACCOUNTS, \OPERATIONS,($< id$, } \\
\text{generateHash($id, code, s$, \TIME'), $code >$ :: \CONTRACTS)], [\PENDING, $<$ (originate contract ${id}$ } \\
\text{transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$), \TIME' $>$ :: \ACCEPTED, updateSucc(\MANAGERS, } \\
\text{$puk, n, m$), ($<$ generateHash($id, code, s$, \TIME'), $n, code$, } \\
 \text{getStorage($code, s$) $>$) :: \CONTRACTORS), \TIME' + 1]$\rangle$}}} 
\end{equation}
~\\
Rule 7 [timeout]:
\begin{equation}{}
\frac{\text{\TIME' - \TIME $\ge$ 60}}{\parbox{4.2in}{\text{[$<$ (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$) $>$ } \\
\text{:: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$[\PENDING, \ACCEPTED, updateCou(\MANAGERS, $puk$, False), \CONTRACTORS, \TIME']}}} 
\end{equation}
~\\
~\\
B. \textbf{Transfer}
\\
~\\
Rule 1 [proposal]:

@@

\begin{equation}{}
\frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ checkPuh(\CONTRACTORS, $puh$)}
\\
\text{ $\wedge$ checkArg(\CONTRACTORS, $puh, s$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}\\
\text{$\rightarrow$  $\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [($<$ (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$), }\\
 \text{generateOph($pkh, puh, s, n, m$, \TIME), \TIME $>$) :: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), }\\
\text{\CONTRACTORS, \TIME] $\rangle$}}} 
\end{equation}
~\\
~\\
Rule 3 [rejected of counter]:

@@

\begin{equation}{}
\frac{\text{$\neg$ checkBal(\MANAGERS, $pkh, n, m$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$ }\\
\text{$\rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 5 [rejected of public hash]:

@@

\begin{equation}
\frac{}{
  \begin{array}{l}
    {[\langle \TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ, \OPH, \TIME
    \rangle :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME']}
    \rightarrow \\
    {}[\PENDING, \langle \TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ, \OPH, \TIME' \rangle :: \ACCEPTED,  \\
    \text{updateSucc(\MANAGERS, \PUK, '', \NTEZ, \MTEZ), updateConstr$(\CONTRACTORS, \PUH, \NTEZ,
  s)$, $\TIME' + 1$]}
  \end{array}
}\label{eq:1}
\end{equation}
~\\
Rule 8 [timeout]:
\begin{equation}{}
\frac{\TIME' - \TIME \ge 60}{\parbox{4.2in}{\text{[transfer $n$ from $puk$ to  $puh$ fee $m$, \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$} \\
\text{[\PENDING, \ACCEPTED, updatecou(\MANAGERS, $puk$, False), \CONTRACTORS, \TIME']}}} 
\end{equation}

\section{Functions}
\begin{enumerate}
    \item Function \verb!checkAcc(pkh, C)! checks whether an account $pkh$ exists in \ACCOUNTS
    \item Function \verb!checkPub(K, pkh)! checks whether the public key of the public key hash $pkh$ is reveled to the blockchain.
    \item Function \verb!checkBal(K, pkh, n, m)! checks whether the balance of the account $pkh$ is greater or equal to $m$ + $n$
    \item Function \verb!checkCou(K, pkh)! checks whether the current
      counter of an account $phk$ is unlocked (i.e., its flag is False)
    \item Function \verb!updateSucc(K, pkh, pkh', n, m)! updates the balance and the counter of the account $phk$ and the balance of the account $phk'$, where
    \begin{itemize}
        \item  \verb!< puk, pkh, bal, (n, True) >!  \verb!=>! \\ \verb!< puk, pkh, bal - n - m, (n + 1, False) >!
        \item  \verb!< puk', pkh', bal', cou' >! \verb!=>! \verb!< puk', pkh', bal' + n, cou' >!
    \end{itemize}

    \item Function \verb!updateCou(K, puk, b')! updates the counter
      lock of the account $phk$ (True $=$ lockeed, False $=$ unlocked), where
    \begin{itemize}
        \item  \verb!< puk, pkh, bal, (n, b) >!  \verb!=>! \verb!< puk, pkh, bal, (n, b') >!
    \end{itemize}

@@

\begin{verbatim}
let rec updateSucc K puk puk' m n =
  match K with
  | 0 -> 0
  | < puk'', bal, cou > :: K' ->
    if (puk = puk'') then < puk'', bal - (n + m), T > 
       :: updateSucc (K', puk, puk', n, m)
    else if (puk' = puk'') then < puk'', bal + n, cou > :: K'
         else  < puk'', bal, cou > 
               ::updateSucc (K', puk, puk', n, m)
\end{verbatim}
